---
title: "viash build"
description: ""
lead: ""
date: 2021-05-28T14:00:00+00:00
lastmod: "`r format(Sys.time(), '%Y-%Om-%dT%H:%M:%S+00:00')`"
draft: false
images: []
menu:
  docs:
    parent: "reference_commands"
weight: 410
toc: true
---

```{r setup, include=FALSE}
library(tidyverse)
source("../../../src/helper/md_helpers.R")

knitr::opts_chunk$set(echo = FALSE)

txt <- extract_help_from_command("build")
```

```{r desc}
knitr::asis_output(extract_description_from_help(txt))
```

Usage: 
```{r usage}
knitr::asis_output(extract_usage_from_help(txt))
```

## Arguments 

### --config  
  
A [viash config file](/docs/reference_config/config) (example: `config.vsh.yaml`). This argument can also be a script with the config as a header.

```{r arg}
knitr::asis_output(extract_arguments_from_help(txt))
```

## Examples

### Building with no arguments

Build a Viash component with only the path to the [viash config file](/docs/reference_config/config) as an argument. 
This will create an 'output' directory and generate an executable inside it with the first platform defined in in your config.
If no platform is found, the [native platform](/docs/reference_config/platform-native) is used:

```bash
viash build config.vsh.yaml
```

### Specifying a platform and an output folder

This builds a Viash component based on your [viash config file](/docs/reference_config/config) in a 'bin' folder that will use Docker to run:

```bash
viash build config.vsh.yaml --platform docker --output "bin"
```

### Using a Docker setup strategy post-build

Create a build for the Docker platform and afterwards execute a `---setup` with a specific [docker setup strategy](/docs/running/executables-docker).

```bash
viash build config.vsh.yaml -p docker --setup alwaysbuild
```

### Print out meta information

Build a Viash component for the native platform and output information about the build in the terminal:

```bash
viash build config.vsh.yaml -p native --meta
```

Here's an example of what the output might look like:

```bash
viash version:      0.5.0
config:             config.vsh.yaml
platform:           native
executable:         output/hello_world
output:             output/
remote git repo:    <NA>
```

### Generate a meta file 

This builds a Viash component and puts a **viash.yaml** file next to the executable containing the full configuration information of the component for later reference:

```bash
viash build config.vsh.yaml --write_meta
```

### Override a config with config mods

Build a Viash component and use a [config mod](/docs/advanced/config_mods) to override the [config file](/docs/reference_config/config).
In this case, pull an image from a docker registry and specify a specific docker registry server URL.

```bash
viash build config.vsh.yaml -p docker \
  -c '.platforms[.type == "docker"].setup_strategy := "pull"' \
  -c '.platforms[.type == "docker"].container_registry := "url-to-registry"'
```

## See also

- [Config file](/docs/reference_config/config)
- [Native platform](/docs/reference_config/platform-native)
- [Docker platform](/docs/reference_config/platform-docker)
- [Executables with a Docker backend](/docs/running/executables-docker)
- [Dynamic Config Modding](/docs/advanced/config_mods)
