---
title: "viash ns build"
description: ""
lead: ""
date: 2021-05-28T14:00:00+00:00
lastmod: "`r format(Sys.time(), '%Y-%Om-%dT%H:%M:%S+00:00')`"
draft: false
images: []
menu:
  docs:
    parent: "reference_commands"
weight: 440
toc: true
---
```{r setup, include=FALSE}
library(tidyverse)
source("../../../src/helper/md_helpers.R")

knitr::opts_chunk$set(echo = FALSE)

# get info from help page
out <- processx::run("viash", c("ns", "build", "-h"))
txt <- out$stdout %>% strsplit("\n") %>% first()
```

```{r desc}
desc <- txt[seq(
  2,
  grep("^Usage:", txt)-2
)] %>% gsub("^viash ", "# viash ", .) %>% 
  paste(., collapse = "\n") %>% 
  detect_links
knitr::asis_output(desc)
```

Usage: 
```{r usage}
usage <- txt[seq(
  grep("^Usage:", txt)+1,
  grep("^Arguments:", txt)-2
)] %>% 
  {paste0("```bash\n", paste(str_trim(.),collapse = "\n"),"\n```\n")} %>% 
  detect_links
knitr::asis_output(usage)
```

## Arguments 

```{r arg}
trail <- grep("^ trailing arguments:", txt)
if (length(trail) == 0) trail <- length(txt)+1
arg <- txt[seq(
  grep("^Arguments:", txt)+1,
  trail-1
)] %>% 
  gsub("\\s\\s(-[^A-Z]*)\\s\\s", "\n### \\1 \n\n", .) %>% 
  gsub(" *$", "", .) %>% 
  paste(., collapse = "\n") %>% 
  detect_links
knitr::asis_output(arg)
```

## Examples

### Building with no arguments

When no arguments are given. All components in a subdirectory named **src** are built with all available platforms to a directory named **target**. 
See [Namespaces](/docs/projects/namespaces) for an overview of how you should structure your components for this to work correctly.  

```bash
viash ns build
```

Here's the output when running this command with three component that support the native and docker platforms:

```bash
Exporting src/parse_images/ (my_namespace) =native=> target/native/my_namespace/parse_images
Exporting src/parse_images/ (my_namespace) =docker=> target/docker/my_namespace/parse_images
Exporting src/download_files/ (my_namespace) =native=> target/native/my_namespace/download_files
Exporting src/download_files/ (my_namespace) =docker=> target/docker/my_namespace/download_files
Exporting src/render_mp4/ (my_namespace) =native=> target/native/my_namespace/render_mp4
Exporting src/render_mp4/ (my_namespace) =docker=> target/docker/my_namespace/render_mp4
```

This is how the structure of the **target** directory might look like after running this command:

```bash
target
├── docker
│   └── my_namespace
│       ├── download_files
│       │   └── download_files
│       ├── parse_images
│       │   └── parse_images
│       └── render_mp4
│           └── render_mp4
└── native
    └── my_namespace
        ├── download_files
        │   └── download_files
        ├── parse_images
        │   └── parse_images
        └── render_mp4
            └── render_mp4
```

### Specifying a source folder and a namespace

In order for namespace querying to work, make sure your config files include a [namespace field](/docs/reference_config/functionality/#namespace-string). 
The command below searches the **my_components_dir** directory for all Viash components in the **my_namespace** namespace and builds them into executables.

```bash
viash ns build --src 'my_components_dir' --query_namespace 'my_namespace'
```

### Filter a specific component to build

This builds any Viash components where the name contains "parse":

```bash
viash ns build --query_name  "parse"
```

### Build targetting a specific platform and an output folder

This builds a Viash namespace for just the [Docker platform](/docs/reference_config/platform-docker) to a directory named **built_namespace**:

```bash
viash ns build --platform docker --target "built_namespace"
```

### Run the build process in parallel

By default, the building of namespaces is a serial process, meaning every components gets built one by one. With the `--parallel` option, you can run the process in parallel, 
allowing you to build all of the components at the same time, potentially saving you a lot of time: 

```bash
viash ns build --parallel
```

### Flatten the output of the build to a single directory

By running the command below, all of the generated executables will be put next to each other in a single directory.    
    
Note: Make sure to define a platform when using the `--flatten` option, the single directory structure doesn't group the executables together per platform. 
Without the `--platform` option, executables will be built for every defined platform and written away to a single file per component, effectively overwriting the same file over and over again.

```bash
viash ns build -p native --flatten
```

The result is a flat target structure: 

```bash
target
├── download_files
├── parse_images
└── render_mp4
```

### Using a Docker setup strategy post-build

Create a build for the Docker platform and afterwards execute a `---setup` with a specific [docker setup strategy](/docs/running/executables-docker).

```bash
viash ns build -p docker --setup alwaysbuild
```

### Generate meta files 

This builds a Viash namespace and puts a **viash.yaml** file next to each executable containing the full configuration information of the component for later reference:

```bash
viash ns build --write_meta
```

### Override a namespace with config mods

Build a Viash namespace and use a [config mod](/docs/advanced/config_mods) to override the [config files](/docs/reference_config/config).

```bash
viash ns build -p docker \
  -c '.platforms[.type == "docker"].setup_strategy := "pull"' \
  -c '.platforms[.type == "docker"].image := "bash:latest"'
```


## See also

- [Config file](/docs/reference_config/config)
- [Dynamic Config Modding](/docs/advanced/config_mods)
- [Native platform](/docs/reference_config/platform-native)
- [Docker platform](/docs/reference_config/platform-docker)
- [Namespaces](/docs/projects/namespaces)
