---
title: "viash ns list"
description: ""
lead: ""
date: 2021-05-28T14:00:00+00:00
lastmod: "`r format(Sys.time(), '%Y-%Om-%dT%H:%M:%S+00:00')`"
draft: false
images: []
menu:
  docs:
    parent: "reference_commands"
weight: 460
toc: true
---

```{r setup, include=FALSE}
library(tidyverse)
source("../../../src/helper/md_helpers.R")

knitr::opts_chunk$set(echo = FALSE)

txt <- extract_help_from_command(c("ns", "list"))
```

```{r desc}
knitr::asis_output(extract_description_from_help(txt))
```

Usage: 
```{r usage}
knitr::asis_output(extract_usage_from_help(txt))
```
## Arguments 

```{r arg}
knitr::asis_output(extract_arguments_from_help(txt))
```

## Examples

### List a namespace without arguments

When no arguments are given, the `ns list` command prints a **parsed** version of all [config files](/docs/reference_config/config) in a subdirectory named **src** to the terminal. 
This includes all fields, even those that were not given values in the config file itself.  
See [Namespaces](/docs/projects/namespaces) for an overview of how you should structure your components for this to work correctly.

```bash
viash ns list
```

After running this command, you'll see a list similar to this:

```bash
- functionality:
    name: "download_files"
    namespace: "my_namespace"
    authors: []
    arguments:
    - type: "string"
      name: "url"
      alternatives: []
      required: false
      direction: "Input"
      multiple: true
      multiple_sep: " "
    - type: "string"
      name: "--filter"
      alternatives: []
      required: false
      direction: "Input"
      multiple: false
      multiple_sep: ":"
    resources:
    - type: "bash_script"
      path: "script.sh"
      is_executable: true
...
```

### Specifying a source folder and a namespace

In order for namespace querying to work, make sure your config files include a [namespace field](/docs/reference_config/functionality/#namespace-string). 
The command below searches the **my_components_dir** directory for all Viash components in the **my_namespace** namespace and prints out the config information to the terminal.

```bash
viash ns list --src 'my_components_dir' -n 'my_namespace'
```

### Filter a specific component to list

This lists any Viash components where the name contains "parse":

```bash
viash ns list --query_name  "parse"
```

### Override a namespace with config mods

List a Viash namespace and use a [config mod](/docs/advanced/config_mods) to override the [config files](/docs/reference_config/config).

```bash
viash ns list -p docker \
  -c '.platforms[.type == "docker"].setup_strategy := "pull"' \
  -c '.platforms[.type == "docker"].image := "bash:latest"'
```

## See also

- [Config file](/docs/reference_config/config)
- [Dynamic Config Modding](/docs/advanced/config_mods)
- [Native platform](/docs/reference_config/platform-native)
- [Docker platform](/docs/reference_config/platform-docker)
- [Namespaces](/docs/projects/namespaces)