---
title: "viash ns list"
description: ""
lead: ""
date: 2021-05-28T14:00:00+00:00
lastmod: "`r format(Sys.time(), '%Y-%Om-%dT%H:%M:%S+00:00')`"
draft: false
images: []
menu:
  docs:
    parent: "reference_commands"
weight: 460
toc: true
---

```{r setup, include=FALSE}
library(tidyverse)
source("../../../src/helper/md_helpers.R")

knitr::opts_chunk$set(echo = FALSE)

# get info from help page
out <- processx::run("viash", c("ns", "list", "-h"))
txt <- out$stdout %>% strsplit("\n") %>% first()
```

```{r desc}
desc <- txt[seq(
  2,
  grep("^Usage:", txt)-2
)] %>% gsub("^viash ", "# viash ", .) %>% 
  paste(., collapse = "\n") %>% 
  detect_links
knitr::asis_output(desc)
```

Usage: 
```{r usage}
usage <- txt[seq(
  grep("^Usage:", txt)+1,
  grep("^Arguments:", txt)-2
)] %>% 
  {paste0("```bash\n", paste(str_trim(.),collapse = "\n"),"\n```\n")} %>% 
  detect_links
knitr::asis_output(usage)
```
## Arguments 

```{r arg}
trail <- grep("^ trailing arguments:", txt)
if (length(trail) == 0) trail <- length(txt)+1
arg <- txt[seq(
  grep("^Arguments:", txt)+1,
  trail-1
)] %>% 
  gsub("\\s\\s(-[^A-Z]*)\\s\\s", "\n### \\1 \n\n", .) %>% 
  gsub(" *$", "", .) %>% 
  paste(., collapse = "\n") %>% 
  detect_links
knitr::asis_output(arg)
```

## Examples

### List a namespace without arguments

When no arguments are given, the `ns list` command prints a **parsed** version of all [config files](/docs/reference_config/config) in a subdirectory named **src** to the terminal. 
This includes all fields, even those that were not given values in the config file itself.  
See [Workflow for creating modular pipelines](/docs/creating_pipelines/modular_pipelines/#building-a-namespace) for an overview of how you should structure your components for this to work correctly.

```bash
viash ns list
```

After running this command, you'll see a list similar to this:

```bash
- functionality:
    name: "download_files"
    namespace: "my_namespace"
    authors: []
    arguments:
    - type: "string"
      name: "url"
      alternatives: []
      required: false
      direction: "Input"
      multiple: true
      multiple_sep: " "
    - type: "string"
      name: "--filter"
      alternatives: []
      required: false
      direction: "Input"
      multiple: false
      multiple_sep: ":"
    resources:
    - type: "bash_script"
      path: "script.sh"
      is_executable: true
...
```

### Specifying a source folder and a namespace

In order for namespace querying to work, make sure your config files include a [namespace field](/docs/reference_config/functionality/#namespace-string). 
The command below searches the **my_components_dir** directory for all Viash components in the **my_namespace** namespace and prints out the config information to the terminal.

```bash
viash ns list --src 'my_components_dir' -n 'my_namespace'
```

### Filter a specific component to list

This lists any Viash components where the name contains "parse":

```bash
viash ns list --query_name  "parse"
```

### Override a namespace with config mods

List a Viash namespace and use a [config mod](/docs/advanced/config_mods) to override the [config files](/docs/reference_config/config).

```bash
viash ns list -p docker \
  -c '.platforms[.type == "docker"].setup_strategy := "pull"' \
  -c '.platforms[.type == "docker"].image := "bash:latest"'
```

## See also

- [Config file](/docs/reference_config/config)
- [Dynamic Config Modding](/docs/advanced/config_mods)
- [Native platform](/docs/reference_config/platform-native)
- [Docker platform](/docs/reference_config/platform-docker)
- [Workflow for creating modular pipelines](/docs/creating_pipelines/modular_pipelines/#building-a-namespace)