---
title: "viash ns test"
description: ""
lead: ""
date: 2021-05-28T14:00:00+00:00
lastmod: "`r format(Sys.time(), '%Y-%Om-%dT%H:%M:%S+00:00')`"
draft: false
images: []
menu:
  docs:
    parent: "reference_commands"
weight: 450
toc: true
---

```{r setup, include=FALSE}
library(tidyverse)
source("../../../src/helper/md_helpers.R")

knitr::opts_chunk$set(echo = FALSE)

txt <- extract_help_from_command(c("ns", "test"))
```

```{r desc}
knitr::asis_output(extract_description_from_help(txt))
```

Usage: 
```{r usage}
knitr::asis_output(extract_usage_from_help(txt))
```

## Arguments 

```{r arg}
knitr::asis_output(extract_arguments_from_help(txt))
```

## Examples

### Testing with no arguments

When no arguments are given. All components in a subdirectory named **src** are tested. This includes testing if a component can be built and any tests defined in its [config file](/docs/reference_config/config). 
See [Namespaces](/docs/projects/namespaces) for an overview of how you should structure your components for this to work correctly.  

```bash
viash ns test
```

After running this command, a test report is printed to the terminal with the results.

### Specifying a source folder and a namespace

In order for namespace querying to work, make sure your config files include a [namespace field](/docs/reference_config/functionality/#namespace-string). 
The command below searches the **my_components_dir** directory for all Viash components in the **my_namespace** namespace and tests them.

```bash
viash ns test --src 'my_components_dir' --query_namespace 'my_namespace'
```

### Filter a specific component to test

This tests any Viash components where the name contains "parse":

```bash
viash ns test --query_name  "parse"
```

### Test a specific platform

This runs a test on all components that utilises the Docker backend: 

```bash
viash ns test --platform docker
```

### Run the tests in parallel

By default, the testing of namespaces is a serial process, meaning every components gets tested one by one. With the `--parallel` option, you can run the process in parallel, 
allowing you to test all of the components at the same time, potentially saving you a lot of time: 

```bash
viash ns test --parallel
```

### Save the test results in a file

You can export the test results to a tab-seperated values (TSV) file with the `--tsv` option. In the example below, a file named **report.tsv** gets generated.

```bash
viash ns test --tsv "report.tsv"
```

## See also

- [Config file](/docs/reference_config/config)
- [Dynamic Config Modding](/docs/advanced/config_mods)
- [Native platform](/docs/reference_config/platform-native)
- [Docker platform](/docs/reference_config/platform-docker)
- [Namespaces](/docs/projects/namespaces)