---
title: "viash ns test"
description: ""
lead: ""
date: 2021-05-28T14:00:00+00:00
lastmod: "`r format(Sys.time(), '%Y-%Om-%dT%H:%M:%S+00:00')`"
draft: false
images: []
menu:
  docs:
    parent: "reference_commands"
weight: 450
toc: true
---

```{r setup, include=FALSE}
library(tidyverse)
source("../../../src/helper/md_helpers.R")

knitr::opts_chunk$set(echo = FALSE)

# get info from help page
out <- processx::run("viash", c("ns", "test", "-h"))
txt <- out$stdout %>% strsplit("\n") %>% first()
```

```{r desc}
desc <- txt[seq(
  2,
  grep("^Usage:", txt)-2
)] %>% gsub("^viash ", "# viash ", .) %>% 
  paste(., collapse = "\n") %>% 
  detect_links
knitr::asis_output(desc)
```

Usage: 
```{r usage}
usage <- txt[seq(
  grep("^Usage:", txt)+1,
  grep("^Arguments:", txt)-2
)] %>% 
  {paste0("```bash\n", paste(str_trim(.),collapse = "\n"),"\n```\n")} %>% 
  detect_links
knitr::asis_output(usage)
```

## Arguments 

```{r arg}
trail <- grep("^ trailing arguments:", txt)
if (length(trail) == 0) trail <- length(txt)+1
arg <- txt[seq(
  grep("^Arguments:", txt)+1,
  trail-1
)] %>% 
  gsub("\\s\\s(-[^A-Z]*)\\s\\s", "\n### \\1 \n\n", .) %>% 
  gsub(" *$", "", .) %>% 
  paste(., collapse = "\n") %>% 
  detect_links
knitr::asis_output(arg)
```

## Examples

### Testing with no arguments

When no arguments are given. All components in a subdirectory named **src** are tested. This includes testing if a component can be built and any tests defined in its [config file](/docs/reference_config/config). 
See [Workflow for creating modular pipelines](/docs/creating_pipelines/modular_pipelines/#building-a-namespace) for an overview of how you should structure your components for this to work correctly.  

```bash
viash ns test
```

After running this command, a test report is printed to the terminal with the results.

### Specifying a source folder and a namespace

In order for namespace querying to work, make sure your config files include a [namespace field](/docs/reference_config/functionality/#namespace-string). 
The command below searches the **my_components_dir** directory for all Viash components in the **my_namespace** namespace and tests them.

```bash
viash ns test --src 'my_components_dir' --query_namespace 'my_namespace'
```

### Filter a specific component to test

This tests any Viash components where the name contains "parse":

```bash
viash ns test --query_name  "parse"
```

### Test a specific platform

This runs a test on all components that utilises the Docker backend: 

```bash
viash ns test --platform docker
```

### Run the tests in parallel

By default, the testing of namespaces is a serial process, meaning every components gets tested one by one. With the `--parallel` option, you can run the process in parallel, 
allowing you to test all of the components at the same time, potentially saving you a lot of time: 

```bash
viash ns test --parallel
```

### Save the test results in a file

You can export the test results to a tab-seperated values (TSV) file with the `--tsv` option. In the example below, a file named **report.tsv** gets generated.

```bash
viash ns test --tsv "report.tsv"
```

## See also

- [Config file](/docs/reference_config/config)
- [Dynamic Config Modding](/docs/advanced/config_mods)
- [Native platform](/docs/reference_config/platform-native)
- [Docker platform](/docs/reference_config/platform-docker)
- [Workflow for creating modular pipelines](/docs/creating_pipelines/modular_pipelines/#building-a-namespace)