---
title: "viash run"
description: ""
lead: ""
date: 2021-05-28T14:00:00+00:00
lastmod: "`r format(Sys.time(), '%Y-%Om-%dT%H:%M:%S+00:00')`"
draft: false
images: []
menu:
  docs:
    parent: "reference_commands"
weight: 400
toc: true
---

```{r setup, include=FALSE}
library(tidyverse)
source("../../../src/helper/md_helpers.R")

knitr::opts_chunk$set(echo = FALSE)

# get info from help page
out <- processx::run("viash", c("run", "-h"))
txt <- out$stdout %>% strsplit("\n") %>% first()
```

```{r desc}
desc <- txt[seq(
  2,
  grep("^Usage:", txt)-2
)] %>% gsub("^viash ", "# viash ", .) %>% 
  paste(., collapse = "\n") %>% 
  detect_links
knitr::asis_output(desc)
```

Usage: 
```{r usage}
usage <- txt[seq(
  grep("^Usage:", txt)+1,
  grep("^Arguments:", txt)-2
)] %>% 
  {paste0("```bash\n", paste(.,collapse = "\n"),"\n```\n")} %>% 
  detect_links
knitr::asis_output(usage)
```

## Arguments 

### --config  
  
A [viash config file](/docs/reference_config/config) (example: `config.vsh.yaml`). This argument can also be a script with the config as a header.

```{r arg}
trail <- grep("^ trailing arguments:", txt)
if (length(trail) == 0) trail <- length(txt)+1
arg <- txt[seq(
  grep("^Arguments:", txt)+1,
  trail-1
)] %>% 
  gsub("^  (-[^A-Z]*)", "\n### \\1 \n\n", .) %>% 
  gsub(" *$", "", .) %>% 
  paste(., collapse = "\n") %>% 
  detect_links
knitr::asis_output(arg)
```

## Examples

Simply run a viash component with its default platform and no script arguments:

```bash
viash run config.vsh.yaml
```

Run a component with script arguments:

```bash
viash run config.vsh.yaml -- --input="Hello!" -o=my_file.txt
```

Here's how you run a viash component using the [Docker platform](/docs/reference_config/platform-docker) and keep the temporary files:

```bash
viash run config.vsh.yaml --platform docker --keep true
```

This example runs a component using the [native platform](/docs/reference_config/platform-native) and passes arguments to the script:

```bash
viash run config.vsh.yaml --platform native -- --input="Hello!" -o=my_file.txt
```

Run a viash component using a [config mod](/docs/reference_config/config_mods) to override the [config file](/docs/reference_config/config). In this case, pull an image from a docker registry and specify a specific docker registry server URL.

```bash
viash run config.vsh.yaml -p docker \
  -c '.platforms[.type == "docker"].setup_strategy := "pull"' \
  -c '.platforms[.type == "docker"].container_registry := "url-to-registry"'
```

## See also

- [Config file](/docs/reference_config/config)
- [Dynamic Config Modding](/docs/reference_config/config_mods)
- [Native platform](/docs/reference_config/platform-native)
- [Docker platform](/docs/reference_config/platform-docker)