---
title: "viash run"
description: ""
lead: ""
date: 2021-05-28T14:00:00+00:00
lastmod: "`r format(Sys.time(), '%Y-%Om-%dT%H:%M:%S+00:00')`"
draft: false
images: []
menu:
  docs:
    parent: "reference_commands"
weight: 400
toc: true
---
```{r setup, include=FALSE}
library(tidyverse)
source("../../../src/helper/md_helpers.R")

knitr::opts_chunk$set(echo = FALSE)

txt <- extract_help_from_command("run")
```

```{r desc}
knitr::asis_output(extract_description_from_help(txt))
```

Usage: 
```{r usage}
knitr::asis_output(extract_usage_from_help(txt))
```

## Arguments 

### \-\-config  
  
A [viash config file](/docs/reference_config/config) (example: `config.vsh.yaml`). This argument can also be a script with the config as a header.

### \-\-verbosity

Executables have 8 levels of verbosity:

- emergency
- alert
- critical
- error
- warning
- notice
- info
- debug

The default verbosity level is **notice**. You can manually set the verbosity by using the `--verbosity <int_level>` option. For example, if you wanted to only show errors or worse:

viash run config.vsh.yaml -- --verbosity 3

### \-v, \-\-verbose

Bump up the verbosity by one level. By passing -vv the verbosity goes up by two levels. 

```{r arg}
knitr::asis_output(extract_arguments_from_help(txt))
```

## Examples

### Running without arguments

Simply run a Viash component with its default platform and no script arguments:

```bash
viash run config.vsh.yaml
```

### Passing script arguments

Run a component with script arguments:

```bash
viash run config.vsh.yaml -- --input="Hello!" -o=my_file.txt
```

### Preserve temporary files

Here's how you run a Viash component using the [Docker platform](/docs/reference_config/platform-docker) and keep the temporary files:

```bash
viash run config.vsh.yaml --platform docker --keep true
```

### Combining run options with script arguments

This example runs a component using the [native platform](/docs/reference_config/platform-native) and passes arguments to the script:

```bash
viash run config.vsh.yaml --platform native -- --input="Hello!" -o=my_file.txt
```

### Override a config with config mods

Run a Viash component using a [config mod](/docs/advanced/config_mods) to override the [config file](/docs/reference_config/config).
In this case, pull an image from a docker registry and specify a specific docker registry server URL.

```bash
viash run config.vsh.yaml -p docker \
  -c '.platforms[.type == "docker"].setup_strategy := "pull"' \
  -c '.platforms[.type == "docker"].container_registry := "url-to-registry"'
```

## See also

- [Config file](/docs/reference_config/config)
- [Dynamic Config Modding](/docs/advanced/config_mods)
- [Native platform](/docs/reference_config/platform-native)
- [Docker platform](/docs/reference_config/platform-docker)