---
title: "viash test"
description: ""
lead: ""
date: 2021-05-28T14:00:00+00:00
lastmod: "`r format(Sys.time(), '%Y-%Om-%dT%H:%M:%S+00:00')`"
draft: false
images: []
menu:
  docs:
    parent: "reference_commands"
weight: 420
toc: true
---


```{r setup, include=FALSE}
library(tidyverse)
source("../../../src/helper/md_helpers.R")

knitr::opts_chunk$set(echo = FALSE)

# get info from help page
out <- processx::run("viash", c("test", "-h"))
txt <- out$stdout %>% strsplit("\n") %>% first()
```

```{r desc}
desc <- txt[seq(
  2,
  grep("^Usage:", txt)-2
)] %>% gsub("^viash ", "# viash ", .) %>% 
  paste(., collapse = "\n") %>% 
  detect_links
knitr::asis_output(desc)
```

Usage: 
```{r usage}
usage <- txt[seq(
  grep("^Usage:", txt)+1,
  grep("^Arguments:", txt)-2
)] %>% 
  {paste0("```bash\n", paste(str_trim(.),collapse = "\n"),"\n```\n")} %>% 
  detect_links
knitr::asis_output(usage)
```

## Arguments 

### --config  
  
A [viash config file](/docs/reference_config/config) (example: `config.vsh.yaml`). This argument can also be a script with the config as a header.

```{r arg}
trail <- grep("^ trailing arguments:", txt)
if (length(trail) == 0) trail <- length(txt)+1
arg <- txt[seq(
  grep("^Arguments:", txt)+1,
  trail-1
)] %>% 
  gsub("\\s\\s(-[^A-Z]*)\\s\\s", "\n### \\1 \n\n", .) %>% 
  gsub(" *$", "", .) %>% 
  paste(., collapse = "\n") %>% 
  detect_links
knitr::asis_output(arg)
```

## Examples

### Running a test with no arguments

Test a viash component with only the path to the [viash config file](/docs/reference_config/config) as an argument. 
This will create a temporary directory in the VIASH_TEMP directory (`/tmp/` by default) and copy over any test files that are specified in the [viash config file](/docs/reference_config/config).  
Next, viash generates an executable inside that directory with the first platform defined in in your config. If no platform is found, the [native platform](/docs/reference_config/platform-native) is used.  
  
Finally, viash will run the test script to do a unit test, with the results being printed out to the terminal.

```bash
viash test config.vsh.yaml
```

### Test a specific platform

This runs a test on a component that utilises the Docker backend: 

```bash
viash test config.vsh.yaml --platform docker
```

### Always keep temporary files after running a test

The command below runs a test and prevents the deletion of temporary files. By default, these files are only retained when an error occured. Setting `keep` to `false` results in the temporary files being deleted in all circumstances. 

```bash
viash test config.vsh.yaml -p native --keep true
```

### Override a config with config mods

Test a viash component while using a [config mod](/docs/reference_config/config_mods) to override the [config file](/docs/reference_config/config).
In this case, pull an image from a docker registry and specify a specific docker registry server URL.

```bash
viash test config.vsh.yaml -p docker \
  -c '.platforms[.type == "docker"].setup_strategy := "pull"' \
  -c '.platforms[.type == "docker"].container_registry := "url-to-registry"'
```

## See also

- [Config file](/docs/reference_config/config)
- [Dynamic Config Modding](/docs/reference_config/config_mods)
- [Native platform](/docs/reference_config/platform-native)
- [Docker platform](/docs/reference_config/platform-docker)